---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(monnouveaupackage)
```
# monnouveaupackage

The goal of monnouveaupackage is to ...
Il a été développé par une équipe de l'[INRA](http://www.inra.fr/).  

Nous aellons voir le versionnage avec cet exemple.

## Installation

You can install the released version of monnouveaupackage from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("monnouveaupackage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
bienvenue("mardi")
```


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r nom_pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

